abc

### 2024-07-07 randpython.qmd
abc

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
filters:
  - webr
---

```{r}
# script/R/simulations.R
```

1.

@@

>>>>

---
title: ""
output: github_document
always_allow_html: true
execute: 
  cache: false
webr:
  show-startup-message: false      # Display status of webR initialization
  show-header-message: false      # Check to see if COOP&COEP headers are set for speed.
  packages: ['dplyr','data.table']             # Pre-install dependencies
filters:
  - panelize
  - webr
  - pyodide
---

```{r}
# https://github.cm/coatless-quarto/panelize
# script/R/simulations.R
# {{< audio file="abc.mp3" caption="Sample Audio File">}}
```

:::{.to-webr}
```{r}
a <- 1 
```
:::

:::{.to-webr}
```{r}
b <- 2
```
:::

:::{.to-webr}
```{r}
c <- a*b
c
```
:::

**Last time updated: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`**

This is a webR-enabled code cell in a Quarto HTML document.

```{webr-r}
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
```

@@

:::{.to-webr}
```{r}
webr::install(c("dplyr","purrr"))
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
dplyr::select(ManifoldDestinyWASMD::abc,S,T,U,V)
library(dplyr)
library(ManifoldDestinyWASMP)
ls("package:dplyr")
ls("package:ManifoldDestinyWASMP")
data(package="ManifoldDestinyWASMD")
```
:::

:::{.to-pyodide}
```{python}
4 + 5
```
:::
